Multisensor Architecture for an Intersection Management System

### 2018-06-18 ch4-results.tex
Updated document structure
Names and captions fixed
brief edit in results chapter

\section{Test Configurations}
In order to test the proposed architecture, three different configurations have been selected. The first configuration is using just one laser sensor. The second configuration is based on multiple laser sensors, Finally, the third configurations uses multiple lasers along with a camera.

Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from sensors, lasers and cameras, to produce an output of higher level. In this case, vehicle counting and intersection occupation level are the metrics used for evaluation.

@@

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c | c| c|}
\hline
\textbf{Block ID} & \textbf{Name} \\
\hline
A & laser\_publisher \\
\hline
B & laser\_bg\_remover \\
\hline
C & laser\_pol2cart \\
\hline
D & laser\_cart\_merge \\
\hline
E & points2clusters \\
\hline
F & clusters\_leg\_counter \\
\hline
G & leg\_counter\_merge \\
\hline
H & clusters2occ\_level \\
\hline
I & occ\_level\_merge \\
\hline
J & laser\_pol2cart \\
\hline
K & points2occgrid \\
\hline
L & occgrid\_merge \\
\hline
M & occgrid\_leg\_counter \\
\hline
N & occgrid2occ\_level \\
\hline
O & camera\_publisher \\
\hline
P & camera\_bg\_remover \\
\hline
Q & camera\_object\_filter \\
\hline
R & camera\_object2occgrid \\
\hline
\end{tabular}
\caption{Description of processing blocks used in test configurations}
\label{desc_test_config}
\end{table}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/4/test_configuration2.pdf}
\caption{Single laser configuration}
\label{tconf2}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/4/test_configuration3.pdf}
\caption{Single laser configuration}
\label{tconf3}
\end{figure}

>>>>

\section{Experimental Setup}

The selected dataset testing the system is POSSi's \ref{possi_ds}. It contains 6 laser-scanners raw readings and a video from a camera located over the intersection. The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears. This groundtruth data was generated by human inspection.

\section{Test Configurations}
In order to test the proposed architecture, three different configurations have been selected. The first configuration is using just one laser sensor. The second configuration is based on multiple laser sensors, Finally, the third configuration uses multiple lasers along with a camera.

Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from sensors, lasers and cameras, to produce an output of higher level. In this case, vehicle counting is the metric used for evaluation.

@@

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c | c| c|}
\hline
\textbf{Block ID} & \textbf{Name} \\
\hline
A & laser\_publisher \\
\hline
B & laser\_bg\_remover \\
\hline
C & laser\_pol2cart \\
\hline
D & laser\_cart\_merge \\
\hline
E & points2clusters \\
\hline
F & clusters\_veh\_counter \\
\hline
G & veh\_counter\_merge \\
\hline
H & clusters2occ\_level \\
\hline
I & occ\_level\_merge \\
\hline
J & laser\_pol2cart \\
\hline
K & points2occgrid \\
\hline
L & occgrid\_merge \\
\hline
M & occgrid\_leg\_counter \\
\hline
N & occgrid2occ\_level \\
\hline
O & camera\_publisher \\
\hline
P & camera\_bg\_remover \\
\hline
Q & camera\_blobs \\
\hline
R & camera\_blobs2occgrid \\
\hline
\end{tabular}
\caption{Description of processing blocks used in test configurations}
\label{desc_test_config}
\end{table}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/4/test_configuration2.pdf}
\caption{Multiple lasers configuration}
\label{tconf2}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/4/test_configuration3.pdf}
\caption{Multiple lasers and camera configuration}
\label{tconf3}
\end{figure}
